My title

### 2024-10-24 paper/paper.qmd
Update paper.

# Create a table showing the prediction results
library(knitr)
kable(state_predictions, col.names = c("State", "Trump Predicted %", "Electoral Votes", "Winner"),
      digits = 2, caption = "Prediction for Trump by State")
```

>>>>

# Create a table showing the prediction results
library(knitr)
kable(state_predictions, col.names = c("State", "Trump Predicted %", "Electoral Votes", "Winner"),
      digits = 2, caption = "Prediction for Trump by State")

# Print the results
print(paste("Trump Electoral Votes:", trump_electoral_votes))
print(paste("Harris Electoral Votes:", harris_electoral_votes))
```

```{r}
summary(regression_model)
```
